% !TEX root = collhdl_ICRA_17.tex

\section{Conclusion}
\label{sec:conclusion}
In this paper, we propose a unified framework for collision detection, isolation and identification of generalized external forces acting along a humanoid robot.
Apart from standard proprioceptive sensing, the proposed scheme makes use of joint torque measurements and acceleration estimates.
Noticeably, it is shown how a generalized momentum observer may be used to calculate these quantities.
As the consequential next step, information from load-compensated force/torque sensors, which can be located arbitrarily along the robot structure, is integrated.
Considering ideal measurements it is shown that estimating the position of a single contact for humanoid robots is possible without any additional sensors.
The positions of multiple concurrent contacts may be estimated with additional force/torque sensors, or, under certain conditions, even without additional sensors.

Future work will cover analyzing the robustness of our scheme in more realistic simulations, in particular with respect to model uncertainties and sensor noise, as well as real world setups.
Also, the complexity and execution time of the algorithm on a real-time enabled system has to be examined closely.
Furthermore, we will investigate the further systematic fusion of joint torque and force/torque sensing in the collision handling context.
Other open questions relate to the thorough yet practical handling of contacts with external moments such as surface contacts and dealing with singularities.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section*{APPENDIX}
%
%% Appendixes should appear before the acknowledgment.


%\section*{ACKNOWLEDGMENT}
